Astr 513: Final Project

### 2016-05-07 Final_Project/ms.tex
best fit plot, fixed autoref

\section{Introduction}
\label{sec:Intro}
Type \rom{1}a supernovae (\snea{}) have been instrumental in the discovery 
of the accelerating expansion of the universe. Presently, {\sn} surveys continue 
to be pivotal in constraining cosmological parameters. In this paper, we present 
our analysis of comparing and combining {\sna} inference of cosmological parameters 
to those from other cosmological probes. In particular, we utilize the constraints 
from the Cosmic Microwave Background (CMB) and the Baryonic Acoustic Oscillations 
(BAO) that are gathered in \citet{planck2013}. We look at two cosmologies in our 
analysis: the $\Lambda \textnormal{CDM}$ universe and the wCDM universe. This 
paper is outlined as follows. In Section 2, the process and importance of {\snea} 
are summarized. A short description of the \Planck mission is given in Section 3. 
Section 4 describe the two {\sna} surveys whose data we use for our analysis. The 
significance of using distance modulus data to constrain cosmological parameters 
is illustrated in Section 5. The CMB and BAO priors taken from \citet{planck2013} 
are also specified in Section 5. Our results and analysis on the benefit of omitting 
or including Bayesian priors from other cosmological probes 
are in Section 6 and Section 7.

@@

\subsection{Planck Priors}
\label{sec:planck_priors}
Our priors are given by the analysis of the \citet{planck2013} data set.
However, instead of simply using the posterior mean and variance of
the parameters from that analysis as priors in our project, we
employed the full \Planck likelihood as a prior. That is,
we first run the Code for Anisotropies in the Microwave Background (CAMB)
in order to obtain the temperature power spectrum $\mathcal{D}_l^{TT}$
and the polarization power spectrum $\mathcal{C}_l^{EE}$
and feed it into the \Planck likelihood code\footnote{More information
on the \Planck likelihood can be found here: 
\url{https://wiki.cosmos.esa.int/planckpla2015/index.php/CMB_spectrum_\%26_Likelihood_Code}.}.
The resulting likelihood
is our prior, and it captures any degeneracies in parameter space
observed by the \Planck analysis, as seen in figure 3.
%\autoref{fig:planck_corner}
\TM{The autoref isn't working here. If someone can figure it out put it back in.}

\begin{figure}
  \label{fig:planck_corner}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/corner_example.eps}
  \caption{\TM{THIS IS A PLACE HOLDER PLOT!}
    Posterior distributions of the cosmological parameter
    analysis using just the \Planck likelihood. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
\end{figure}

\subsection{CosmoSIS}
\label{sec:CosmoSIS}
\CosmoSIS is a framework that connects multiple existing codes as 
modules in order to do cosmological parameter estimation. Users 
can utilize existing codes or use their own codes for modules. For 
our analysis, \CosmoSIS provides a convenient way to link together 
CAMB, the \Planck likelihood code (our priors), and our {\sn} likelihood 
code in a single pipeline. This design choice minimized the significant
time that would inevitably have been spent on connecting these 
independently-made programs into one, allowing us to focus on 
doing science rather than software development.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_bestfit.eps}
  \caption{Best fit model of the \citet{betoule2014} data including the
    \Planck priors for a wCDM model. Blue points are the data with
    error bars corresponding to the diagonal of the provided covariance martrix.
    The solid black line is the most likely model from our MCMC chain.}
  \label{fig:betoule_wcdm_noprior_bestfit}
\end{figure}

>>>>

\section{Introduction}
\label{sec:Intro}
Type \rom{1}a supernovae (\snea{}) have been instrumental in the discovery 
of the accelerating expansion of the universe. Presently, {\sn} surveys continue 
to be pivotal in constraining cosmological parameters. In this paper, we present 
our analysis of comparing and combining {\sna} inference of cosmological parameters 
to those from other cosmological probes. In particular, we utilize the constraints 
from the Cosmic Microwave Background (CMB) and the Baryonic Acoustic Oscillations 
(BAO) that are gathered in \citet{planck2013}. We look at two cosmologies in our 
analysis: the $\Lambda \textnormal{CDM}$ universe and the $w$CDM universe. This 
paper is outlined as follows. In Section 2, the process and importance of {\snea} 
are summarized. A short description of the \Planck mission is given in Section 3. 
Section 4 describe the two {\sna} surveys whose data we use for our analysis. The 
significance of using distance modulus data to constrain cosmological parameters 
is illustrated in Section 5. The CMB and BAO priors taken from \citet{planck2013} 
are also specified in Section 5. Our results and analysis on the benefit of omitting 
or including Bayesian priors from other cosmological probes 
are in Section 6 and Section 7.

@@

\subsection{Planck Priors}
\label{sec:planck_priors}
Our priors are given by the analysis of the \citet{planck2013} data set.
However, instead of simply using the posterior mean and variance of
the parameters from that analysis as priors in our project, we
employed the full \Planck likelihood as a prior. That is,
we first run the Code for Anisotropies in the Microwave Background (CAMB)
in order to obtain the temperature power spectrum $\mathcal{D}_l^{TT}$
and the polarization power spectrum $\mathcal{C}_l^{EE}$
and feed it into the \Planck likelihood code\footnote{More information
on the \Planck likelihood can be found here: 
\url{https://wiki.cosmos.esa.int/planckpla2015/index.php/CMB_spectrum_\%26_Likelihood_Code}.}.
The resulting likelihood
is our prior, and it captures any degeneracies in parameter space
observed by the \Planck analysis, as seen in \autoref{fig:planck_corner}. 
%
\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/corner_example.eps}
  \caption{Posterior distributions of the cosmological parameter
    analysis using just the \Planck likelihood. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:planck_corner}
\TM{THIS IS A PLACE HOLDER PLOT!} 
\end{figure}
%

\subsection{CosmoSIS}
\label{sec:CosmoSIS}
\CosmoSIS is a framework that connects multiple existing codes as 
modules in order to do cosmological parameter estimation. Users 
can utilize existing codes or use their own codes for modules. For 
our analysis, \CosmoSIS provides a convenient way to link together 
CAMB, the \Planck likelihood code (our priors), and our {\sna} likelihood 
code in a single pipeline. This design choice minimized the significant
time that would inevitably have been spent on connecting these 
independently-made programs into one, allowing us to focus on 
doing science rather than software development.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_bestfit.eps}
  \caption{Best fit model of the \citet{betoule2014} data including the
    \Planck priors for a $w$CDM model. Blue points are the data with
    error bars corresponding to the diagonal of the provided covariance martrix.
    The solid black line is the most likely model from our MCMC chain.}
  \label{fig:betoule_wcdm_prior_bestfit}
\end{figure}
